\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-04-20 adaptive-estimation.tex
addressed specific commets in R2

More formally, we consider the following estimation scheme. Given
$n_1 \in \{1, \ldots, n\}$,
set the individual bits
\begin{equation*}
  B_i =
  \begin{cases}
    \indic{X_i \le \theta_0} & i = 1,\ldots,n_1, \\
    \indic{X_i \le T_n}& i={n_1+1,\ldots,n},
  \end{cases}
\end{equation*}
where
\begin{equation*}
  T_n \defeq \theta_0 - F^{-1}\left(
  \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
  \right)
  ~~ \mbox{and} ~~
  \theta_n \defeq
  T_n - F^{-1} \left(\frac{1}{n - n_1}
  \sum_{i = n_1}^n B_i \right).
\end{equation*} 
The intuition here is that the estimator $\theta_n$ is a one-step
correction (cf.~\cite[Thm.~6.4.3]{LehmannCa98}) of the initial estimator
$T_n$, which approximately estimates
$\theta_0 - F^{-1}(\theta_0 - \theta) = \theta$. We then have the
following convergence result.
\begin{thm}
  Assume that $X_i = Z_i + \theta$, where $Z_i$ are i.i.d.\
  with density $f$ and CDF $F$ and $\mbox{med}(Z_i) = 0$. Assume that
  $f$ is continuous at 0, and that as $n \to \infty$,
  $n_1(n) \rightarrow \infty$ and $n_1 / n \to
  0$. Then
  \begin{align*}
    \sqrt{n} \left( {\theta}_n - \theta  \right)
    \cd  \normal\left( 0, \frac{1}{4 f(0)^2}\right).
  \end{align*}
\end{thm}
\noindent
That is, under Assumption~\ref{assump:failure_rate}, the method is
asymptotically optimal.
%
\begin{proof}
  We abuse notation and instead of assuming we receive $n$ observations, assume
  we receive the $n + n_1$ observations $X_{-n_1}, \ldots, X_{-1}$ and
  $X_1, \ldots, X_n$, defining $T_n = \theta_0 - F^{-1}(\frac{1}{n_1}
  \sum_{i = -n_1}^{-1} B_i)$ and
  $B_i = \indic{X_i \le T_n}$ for $i \ge 1$.
  Letting $X_i = Z_i + \theta$ for $Z_i$ i.i.d.\ with fixed density
  $f = F'$, we have
  $\ex{B_i} \cas F(\theta_0 - \theta)$, so that
  $\frac{1}{n_1} \sum_{i = -n_1}^{-1} B_i \cas F(\theta - \theta_0)$ and
  by the continuous
  mapping theorem we have $T_n \cas \theta$ as $n_1 \to \infty$.

  Now let
  $E_n = \E[B_i \mid T_n] = P(X_i \le T_n)$,
  so that $\var(B_i \mid T_n) = E_n(1 - E_n)$. Define also the random
  variable
  \begin{equation*}
    Y_n \defeq \sqrt{n}
    \frac{1}{\sqrt{E_n (1 - E_n)}}
    \bigg[\frac{1}{n}\sum_{i = 1}^n B_i - E_n\bigg],
  \end{equation*}
  and let $F_n(\cdot \mid T_n)$ be its cumulative distribution function.
  Then because
  \begin{equation*}
    \E\left[|B_i - E_n|^3 \mid T_n\right] \le E_n(1 - E_n)
    ~~ \mbox{we have} ~~
    \E\left[\frac{|B_i - E_n|^3}{(E_n(1 - E_n))^{3/2}} \mid T_n\right]
    \le \frac{1}{\sqrt{E_n(1 - E_n)}}.
  \end{equation*}
 The Berry-Esseen theorem implies that there exists a constant
  $C \le 1$ such that
  \begin{equation*}
    \sup_t \left|F_n(t \mid T_n) - \Phi(t) \right|
    \le \frac{C}{\sqrt{E_n (1 - E_n)} \sqrt{n}} \wedge 2,
  \end{equation*}
  where $\Phi$ is the standard Gaussian CDF.
  As $E_n (1 - E_n) \cas \frac{1}{4}$ by definition of the median,
  we have
  that (with probability 1)
  \begin{equation*}
    \sup_t \left|F_n(t \mid T_n) - \Phi(t)\right| \le \frac{C}{\sqrt{n}}
    ~~ \mbox{eventually}.
  \end{equation*}
  By dominated convergence and Jensen's inequality we thus obtain
  \begin{equation*}
    \sup_t \left|\mathbb{P}(Y_n \le t) - \Phi(t)\right|
    \le \E\left[
      \sup_t \left|F_n(t \mid T_n) - \Phi(t)\right| \right]
    \to 0,
  \end{equation*}
  which gives that $Y_n \cd \normal(0, 1)$.

  Now,
  Slutsky's lemmas imply
  \begin{equation}
    \sqrt{n}
    \cdot \frac{2}{n} \sum_{i = 1}^n (B_i - E_n)
    =
    (1 + o_P(1)) \frac{1}{\sqrt{n E_n(1 - E_n)}}
    \sum_{i = 1}^n \left(B_i - E_n\right)
    \cd \normal(0, 1).
    \label{eqn:apply-slutsky}
  \end{equation}
  For shorthand we write $P_n B = \frac{1}{n} \sum_{i = 1}^n B_i$,
  and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may thus
  use the delta method to write
  \begin{align*}
    \sqrt{n}(\theta_n - \theta)
    & = \sqrt{n}\left(T_n - F^{-1}\left(P_n B\right)
    - \theta \right) \\
    & = \sqrt{n} \left(T_n - F^{-1}\left(F(T_n - \theta)
    + P_n B - F(T_n - \theta)\right) - \theta \right) \\
    & = \sqrt{n} \left(T_n - (T_n - \theta )
    + (F^{-1})'(T_n - \theta + o_P(1))\cdot \left(
    P_n B - E_n\right) - \theta \right) \\
    & = \sqrt{n} (F^{-1})'(0) (P_n B - E_n)
    + o_P(1)
    \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
  \end{align*}
  where we have used the limiting distribution~\eqref{eqn:apply-slutsky}. 
\end{proof}
%

>>>>

More formally, we consider the following estimation scheme. Given
$n_1 \in \{1, \ldots, n\}$,
set the individual bits
\begin{equation*}
  B_i =
  \begin{cases}
    \indic{X_i \le \theta_0} & i = 1,\ldots,n_1, \\
    \indic{X_i \le T_n}& i={n_1+1,\ldots,n},
  \end{cases}
\end{equation*}
where
\begin{align*}
  T_n & \defeq \theta_0 - F^{-1}\left(
  \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
  \right)\\
  \theta_n & \defeq
  T_n - F^{-1} \left(\frac{1}{n - n_1}
  \sum_{i = n_1}^n B_i \right).
\end{align*} 
The intuition here is that the estimator $\theta_n$ is a one-step
correction (cf.~\cite[Thm.~6.4.3]{LehmannCa98}) of the initial estimator
$T_n$, which approximately estimates
$\theta_0 - F^{-1}\left(F(\theta_0 - \theta)\right) = \theta$. We then have the
following convergence result.
\begin{thm}
  Assume that $X_i = Z_i + \theta$, where $Z_i$ are i.i.d.\
  with density $f$ and CDF $F$ and $\mbox{med}(Z_i) = 0$. Assume that
  $f$ is continuous at 0, and that as $n \to \infty$,
  $n_1(n) \rightarrow \infty$ and $n_1 / n \to
  0$. Then
  \begin{align*}
    \sqrt{n} \left( {\theta}_n - \theta  \right)
    \cd  \normal\left( 0, \frac{1}{4 f(0)^2}\right).
  \end{align*}
\end{thm}
\noindent
That is, under Assumption~\ref{assump:failure_rate}, the method is
asymptotically optimal.
%
\begin{proof}
  We abuse notation and instead of assuming we receive $n$ observations, assume
  we receive the $n + n_1$ observations $X_{-n_1}, \ldots, X_{-1}$ and
  $X_1, \ldots, X_n$, defining $T_n = \theta_0 - F^{-1}(\frac{1}{n_1}
  \sum_{i = -n_1}^{-1} B_i)$ and
  $B_i = \indic{X_i \le T_n}$ for $i \ge 1$.
  Letting $X_i = Z_i + \theta$ for $Z_i$ i.i.d.\ with fixed density
  $f = F'$, we have
  $\ex{B_i} \cas F(\theta_0 - \theta)$, so that
  $\frac{1}{n_1} \sum_{i = -n_1}^{-1} B_i \cas F(\theta - \theta_0)$ and
  by the continuous
  mapping theorem we have $T_n \cas \theta$ as $n_1 \to \infty$.

  Now let
  $E_n = \E[B_i \mid T_n] = P(X_i \le T_n)$,
  so that $\var(B_i \mid T_n) = E_n(1 - E_n)$. Define also the random
  variable
  \begin{equation*}
    Y_n \defeq \sqrt{n}
    \frac{1}{\sqrt{E_n (1 - E_n)}}
    \bigg[\frac{1}{n}\sum_{i = 1}^n B_i - E_n\bigg],
  \end{equation*}
  and let $F_n(\cdot \mid T_n)$ be its cumulative distribution function.
  Then because
  \begin{equation*}
    \E\left[|B_i - E_n|^3 \mid T_n\right] \le E_n(1 - E_n),
    \end{equation*}
      we have 
\begin{equation*}
    \E\left[\frac{|B_i - E_n|^3}{(E_n(1 - E_n))^{3/2}} \mid T_n\right]
    \le \frac{1}{\sqrt{E_n(1 - E_n)}}.
  \end{equation*}
 The Berry-Esseen theorem implies that there exists a constant
  $C \le 1$ such that
  \begin{equation*}
    \sup_t \left|F_n(t \mid T_n) - \Phi(t) \right|
    \le \frac{C}{\sqrt{E_n (1 - E_n)} \sqrt{n}} \wedge 2,
  \end{equation*}
  where $\Phi$ is the standard Gaussian CDF.
  As $E_n (1 - E_n) \cas \frac{1}{4}$ by definition of the median,
  we have
  that (with probability 1)
  \begin{equation*}
    \sup_t \left|F_n(t \mid T_n) - \Phi(t)\right| \le \frac{C}{\sqrt{n}}
    ~~ \mbox{eventually}.
  \end{equation*}
  By dominated convergence and Jensen's inequality we thus obtain
  \begin{equation*}
    \sup_t \left|\mathbb{P}(Y_n \le t) - \Phi(t)\right|
    \le \E\left[
      \sup_t \left|F_n(t \mid T_n) - \Phi(t)\right| \right]
    \to 0,
  \end{equation*}
  which gives that $Y_n \cd \normal(0, 1)$. Now, Slutsky's lemmas imply
  \begin{align}
    &\sqrt{n}
    \cdot \frac{2}{n} \sum_{i = 1}^n (B_i - E_n)
    \\
    & \qquad  =
 \frac{1 + o_P(1)}{\sqrt{n E_n(1 - E_n)}}
    \sum_{i = 1}^n \left(B_i - E_n\right)
    \cd \normal(0, 1).
    \label{eqn:apply-slutsky}
  \end{align}
  where $o_P(1)$ denotes sequence of random variables converging to zero in probability as $n$ goes to infinity. With $\bar{B}_n \defeq \frac{1}{n} \sum_{i = 1}^n B_i$ and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may use the delta method to write
  \begin{align*}
    & \sqrt{n}(\theta_n - \theta)
     = \sqrt{n}\left(T_n - F^{-1}\left( \bar{B}_n \right)
    - \theta \right) \\
    &\quad  = \sqrt{n} \left[T_n - F^{-1}\left(F(T_n - \theta)
    + \bar{B}_n - F(T_n - \theta)\right) - \theta \right] \\
    & \quad = \sqrt{n} \left[ T_n - (T_n - \theta ) \right. \\
    &  \left. +  (F^{-1})' \left(T_n - \theta + o_P(1) \right)  
    \cdot \left(\bar{B}_n - E_n\right) - \theta \right] \\
    & \quad = \sqrt{n} (F^{-1})'(0) ( \bar{B}_n - E_n)
    + o_P(1) \\
    & \quad \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
  \end{align*}
  where we have used the limiting distribution~\eqref{eqn:apply-slutsky}. 
\end{proof}
%

### 2022-04-20 conclusions.tex
addressed specific commets in R2

\newtext{
Natural extensions of the setting of this work are situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector. Rough bounds in this general case follow from several recent works (e.g. \cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), which imply that in the adaptive and distributed cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$. Nevertheless, the coefficients of the $1/n$ term corresponding to the ARE are in general unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.}

>>>>

Natural extensions of this work include situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector. Bounds on rate of convergence of the MSE in this general case follow from several recent works (e.g. \cite{zhang2013information,shamir2014fundamental,
braverman2016communication,han2018geometric,
barnes2020lower,cai2020distributed}), that in particular imply that in some cases the MSE decreases in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$. Nevertheless, the coefficient of the leading $1/n$ term corresponding to the ARE, which we characterized here in the case $b=1$ and $d=1$, is still unknown in the general case.

### 2022-04-20 distributed-estimation.tex
addressed specific commets in R2

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under the adaptive signal acquisition setting,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed-form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

@@

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\input{Figs/opt_thr_den.tex}
\caption{\label{fig:minimax_support}
Optimal threshold density under distributed encoding. The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x)$ the normal desnity with variance $\sigma^2$ and $\Theta= [-1/2,1/2]$. 
%
The continuous curve (red) is the ARE for each $\theta \in [-1/2,1/2]$ under the optimal density, hence the minimax ARE is the minimal value of this curve. The dashed curve (green) is the ARE when the threshold values are uniformly distributed over $[-1/2,1/2]$; its minimal value is $\kappa_{\unif}$ \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

@@

\addplot[color = black!35!green, dashed, line width=1.0pt,
        %mark size=1.5pt, mark=^
        ]
 plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{\scriptsize uniform threshold desnity};

>>>>

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under the adaptive signal acquisition setting,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed-form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{align}
  L_n(A_1,\ldots,A_n;\theta)
  & = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) } \\
  & = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{align}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

@@

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\input{Figs/opt_thr_den.tex}
\caption{\label{fig:minimax_support}
Optimal threshold density under distributed encoding. The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x)$ the normal density with variance $\sigma^2$ and $\Theta= [-1/2,1/2]$. 
%
The continuous curve (red) is the ARE for each $\theta \in [-1/2,1/2]$ under the optimal density, hence the minimax ARE is the minimal value of this curve. The dashed curve (green) is the ARE when the threshold values are uniformly distributed over $[-1/2,1/2]$; its minimal value is $\kappa_{\unif}$ \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

@@

\addplot[color = black!35!green, dashed, line width=1.0pt,
        %mark size=1.5pt, mark=^
        ]
 plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{\scriptsize uniform threshold density};

### 2022-04-20 onebit_full.tex
addressed specific commets in R2

%% \documentclass[11pt]{article}
\documentclass[letterpaper, 11pt, draftcls]{IEEEtran}      % Use this line for a4 paper

@@

\author{
    \IEEEauthorblockN{
Alon Kipnis\IEEEauthorrefmark{1} and   
    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }

\thanks{This paper was presented in part at the 55th Annual Allerton Conference on Communication, Control, and Computing (Allerton) \cite{KipnisAllerton2017}.
}
}

%% \renewenvironment{figure}{%
%%   \ignorespaces
%% }{}

@@

\section*{Acknowledgments}
%% \textbf{WRITE THIS SECTION}
The work of A. Kipnis was supported in part by funding from the NSF under Grant No.~DMS-1418362 and DMS-1407813, and by a fellowship from the Koret Foundation.

>>>>

%% \documentclass[11pt]{article}
\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper

@@

\author{
    \IEEEauthorblockN{
Alon Kipnis and   
    John C. Duchi }

\thanks{
Alon Kipnis is with the School of Computer Science at Reichman University, Herzliya, Israel (kipnisal@stanford.edu).} 
\thanks{J. Duchi is with the Department of Statistics and Department of Electrical Engineering at Stanford University, Stanford, CA, 94035 (jduchi@stanford.edu).}
\thanks{Copyright (c) 2017 IEEE. Personal use of this material is permitted.  However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
\thanks{This paper was presented in part at the 55th Annual Allerton Conference on Communication, Control, and Computing (Allerton) \cite{KipnisAllerton2017}. }
\thanks{
The work of A. Kipnis was supported in part by funding from the NSF under Grant No.~DMS-1418362 and DMS-1407813, and by a fellowship from the Koret Foundation.}
}

@@

### 2022-04-20 preliminaries.tex
ready for submission
fixed all minor comments from R1
addressed specific commets in R2

\subsection{Consistent Estimation}
The simplest estimator is simply to invert a quantile. Indeed,
fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
\[
B_i = \mathbf 1_{X_i<\theta_0}, 
\]
where $\mathbf 1_A$ is the indicator of the event $A$. We have
\[
P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta_0 - \theta),  
\]
so that 
\begin{equation}
\label{eq:estimator_naive}
{\theta}_n = \theta_0 - F^{-1}\left( P_n \right)
\end{equation}
is a consistent estimator for $\theta$ in the distributed setting of
Figure~\ref{fig:setup}-(iii), where we note that $F$ is invertible over the
support of $f$. As the variance of $P_n$ is
$F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)$, a delta method
calculation~\cite[Ch.~23]{VanDerVaart98} implies that ${\theta}_n$ is
asymptotically normal with variance
\begin{equation*}
  \frac{F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)}{f^2(\theta_0-\theta)} = \frac{1}{
\eta(\theta_0-\theta)}.
\end{equation*}
In the Gaussian case where the $X_i \simiid \normal(\theta, \sigma^2)$, the
ARE of ${\theta}_n$ is $\eta(\theta_0 - \theta)\sigma^2$.

@@

When the prior on $\theta$ and the noise corrupting it at each location are
Gaussian, Prabhakaran et al.~\cite{prabhakaran2004rate} characterize the
optimal encoding and its asymptotic risk as $k \to \infty$.  Chen et
al.~\cite{chen2004upper} also provide an expression for the quadratic risk
in the CEO setting under Gaussian priors. Adapting to our setting, this
expression provides the following proposition:
\begin{prop} \label{prop:CEO}
  Assume that $\Theta = \mathbb R$ and $\pi(\theta) =
  \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is
  arbitrary. Then any estimator ${\theta}_n$ of $\theta$ in the distributed
  setting satisfies
  \begin{equation} \label{eq:ceo_bound}
    n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
  \end{equation}
  where the expectation is with respect to $\theta$ and $X_1,\ldots,X_n$.
\end{prop}
\noindent
See Appendix~\ref{app:proof:CEO} for a proof.

>>>>

\subsection{Consistent Estimation}
The simplest estimator is simply to invert a quantile. Indeed,
fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
\[
B_i = \indic{X_i<\theta_0}, 
\]
where $\indic{A}$ is the indicator of the event $A$. We have
\[
\bar{B}_n \defeq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta_0 - \theta),  
\]
so that 
\begin{equation}
\label{eq:estimator_naive}
{\theta}_n = \theta_0 - F^{-1}\left( \bar{B}_n \right)
\end{equation}
is a consistent estimator for $\theta$ in the distributed setting of
Figure~\ref{fig:setup}-(iii), where we note that $F$ is invertible over the
support of $f$. As the variance of $\bar{B}_n$ is
$F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)$, a delta method
calculation~\cite[Ch.~23]{VanDerVaart98} implies that ${\theta}_n$ is
asymptotically normal with variance
\begin{equation*}
  \frac{F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)}{f^2(\theta_0-\theta)} = \frac{1}{
\eta(\theta_0-\theta)}.
\end{equation*}
In the Gaussian case where the $X_i \simiid \normal(\theta, \sigma^2)$, the
ARE of ${\theta}_n$ is $\eta(\theta_0 - \theta)\sigma^2$.

@@

When the prior on $\theta$ and the noise corrupting it at each location are
Gaussian, Prabhakaran et al.~\cite{prabhakaran2004rate} characterize the
optimal encoding and its asymptotic risk as $k \to \infty$.  Chen et
al.~\cite{chen2004upper} also provide an expression for the quadratic risk
in the CEO setting under Gaussian priors. Adapting to our setting, this
expression provides the following proposition:
\begin{prop} \label{prop:CEO}
  Assume that $\Theta = \mathbb R$ and $\pi(\theta) =
  \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is
  arbitrary. Then any estimator ${\theta}_n$ of $\theta$ in the distributed
  setting satisfies
  \begin{equation} \label{eq:ceo_bound}
    n \cdot \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
  \end{equation}
  where the expectation is with respect to $\theta$ and $X_1,\ldots,X_n$.
\end{prop}
\noindent
See Appendix~\ref{app:proof:CEO} for a proof.
